\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-03 doc/flexiblesusy-paper.tex
correcting nightly test results url
add refeence for Softsusy 3.5.0

To check the correctness of \fs's generated spectrum generators
extensive unit testing against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
was carried out.  These unit tests systematically compare all
tree-level mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles numerically for certain MSSM and NMSSM parameter
points.  All tested expressions were found to agree within double
machine precision.\footnote{Due to the systematic and detailed tests
  several bugs in Softsusy, SARAH and \fs could be identified and
  corrected.}  Furthermore, the overall pole mass spectrum after the
full fixed-point iteration has finished is compared, and was found to
agree at the sub-permille level.  The origin of the sub-permille level
difference between \fs and Softsusy is the different determination of
the \DRbar\ weak mixing angle
$\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$: \fs calculates
$\theta_W$ from $M_W^2$ and $M_Z^2$ as described in
\secref{sec:calculation-of-gauge-couplings}, while Softsusy determines
$\theta_W$ from the muon decay constant $G_\mu$, which is more
precise.  Furthermore, in Softsusy $3.5.0$ some three-loop
$\beta$-functions and two-loop threshold corrections for the gauge and
Yukawa couplings can be enabled in the MSSM to increase the accuracy
of the RG running and the \DRbar\ gauge and Yukawa couplings at $M_Z$
\cite{}.  These corrections are not implemented in \fs so far.

The complete set of unit tests is shipped with \fs and can be found in
the \code{test/} directory.  The tests can be run with the command
\code{make execute-tests}.  All unit tests are carried out nightly in
order to continuously check the correctness of the meta code and the
generated spectrum generators.  The test results can be found at
\url{http://iktp.tu-dresden.de/~avoigt/FlexibleSUSY/FlexibleSUSY/test.html}

@@

>>>>

To check the correctness of \fs's generated spectrum generators
extensive unit testing against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
was carried out.  These unit tests systematically compare all
tree-level mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles numerically for certain MSSM and NMSSM parameter
points.  All tested expressions were found to agree within double
machine precision.\footnote{Due to the systematic and detailed tests
  several bugs in Softsusy, SARAH and \fs could be identified and
  corrected.}  Furthermore, the overall pole mass spectrum after the
full fixed-point iteration has finished is compared, and was found to
agree at the sub-permille level.  The origin of the sub-permille level
difference between \fs and Softsusy is the different determination of
the \DRbar\ weak mixing angle
$\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$: \fs calculates
$\theta_W$ from $M_W^2$ and $M_Z^2$ as described in
\secref{sec:calculation-of-gauge-couplings}, while Softsusy determines
$\theta_W$ from the muon decay constant $G_\mu$, which is more
precise.  Furthermore, in Softsusy $3.5.0$ some three-loop
$\beta$-functions and two-loop threshold corrections for the gauge and
Yukawa couplings can be enabled in the MSSM to increase the accuracy
of the RG running and the determination of the \DRbar\ gauge and
Yukawa couplings at $M_Z$ \cite{Allanach:2014nba}.  These corrections
are not implemented in \fs so far.

The complete set of unit tests is shipped with \fs and can be found in
the \code{test/} directory.  The tests can be run with the command
\code{make execute-tests}.  All unit tests are carried out nightly in
order to continuously check the correctness of the meta code and the
generated spectrum generators.  The test results can be found at
\url{http://iktp.tu-dresden.de/~avoigt/FlexibleSUSY/test.xhtml}

@@

\bibitem{Allanach:2014nba}
  B.~C.~Allanach, A.~Bednyakov and R.~Ruiz de Austri,
  %``Higher Order Corrections and Unification in the Minimal Supersymmetric Standard Model: SOFTSUSY3.5.0,''
  arXiv:1407.6130 [hep-ph].
  %%CITATION = ARXIV:1407.6130;%%
  %2 citations counted in INSPIRE as of 03 Nov 2014
